\documentclass[titlepage]{octavo}
\usepackage[lmargin=1.8cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{lettrine}
\usepackage{tgchorus}
\usepackage[T1]{fontenc}
\usepackage{niceframe}
\usepackage{parselines}
\usepackage{xcolor}
\definecolorseries{verso}{rgb}{last}{blue!40!black}{magenta!40!black}
\resetcolorseries[30]{verso}

\newenvironment{verso}{\pagebreak[3]\begin{parse lines}[\parindent=1em\noindent]{\color{verso!!+}\hspace{\row\parindent}##1\newline\color{black}}}%
{\end{parse lines}}


\title{My \LaTeX{} \emph{poetry}}
\author{by Fabien Le Mentec}
\date{}

\pagestyle{empty}
\setcounter{secnumdepth}{-1}
\setcounter{tocdepth}{1}

\begin{document}

\begin{titlepage}
\begin{center}
\vfill 

\Huge \fontsize{75}{60}\selectfont
\artdecoframe{\emph{Poems}}
\vfill 
\large\emph{By Fabien Le Mentec} 
\vfill
\end{center}
\end{titlepage}

\curlyframe{\vspace{-8ex}\tableofcontents\vspace{8ex}}

\pagebreak 
\section{\dotfill Made Of Ink}
\large

\resetcolorseries[16]{verso}
\begin{verso}
\makebox[.6em][c]{\lettrine{H}{}}ere, what's not white
Is filled with black.
No striking light
No fading dark.
\end{verso}

\begin{verso}
There is no joy
In what I think.
'Cause I'm a boy
All made of ink.
\end{verso}

\hfill{17 December 2014}

\pagebreak
\section{\dotfill Inertia}
\large

\resetcolorseries[24]{verso}
\begin{verso}
\makebox[1em][c]{\lettrine{T}{}}here is no shame in getting lost
What is foolish, is staying frost.
Waiting for things, 'till it's too late,
So find your path, fulfill your fate.
\end{verso}

\hfill{1 January 2015}

\pagebreak
\section{\dotfill La Mer}
\large

\resetcolorseries[24]{verso}
\begin{verso}
\makebox[1em][c]{\lettrine{A}{}} l'horizon, la mer s'\'etend,
Grise et verd\^atre, battue au vent.
\end{verso}

\begin{verso}
Seul sur le sable, la mer m'appelle,
Et je me sens comme infid\`ele.
\end{verso}

\begin{verso}
T'aurais je rat\'e, ma destin\'ee ?
Ouvert \`a toi, mon coeur bless\'e.
\end{verso}

\hfill{26 September 2016}

\pagebreak
\section{\dotfill L'Oiseau Des Mers}
\large

\resetcolorseries[24]{verso}
\begin{verso}
\makebox[1em][c]{\lettrine{T}{}}el un oiseau, qui glisse dans l'air,
Mais tes courants, sont ceux des mers.
\end{verso}

\begin{verso}
Qu'est ce qui l\`a haut, t'a fait plong\'e,
Pour ne jamais y retourner ?
\end{verso}

\begin{verso}
D'un battement d'ailes, tu continues,
Vers le grand bleu, vers l'inconnu.
\end{verso}

\hfill{27 September 2016}

\pagebreak
\section{\dotfill Trop}
\large

\resetcolorseries[24]{verso}
\begin{verso}
\makebox[1em][c]{\lettrine{T}{}}rop \`a babord,
Trop vers le Nord,
Trop loin du port,
Trop pr\^et des morts.
\end{verso}

\hfill{27 September 2016}


\pagebreak
\section{\dotfill Synchrotron Light}
\large

\resetcolorseries[24]{verso}
\begin{verso}
\makebox[1em][c]{\lettrine{W}{}}ith high voltage the electrons,
Escape as balls from the canons.
\end{verso}

\begin{verso}
They are then accelerated,
Approaching even Light in speed.
\end{verso}

\begin{verso}
Magnetic fields make them deviate,
Loose energy, and radiate.
\end{verso}

\begin{verso}
In the beamlines through slits and glass,
Colors are tuned as the rays pass.
\end{verso}

\begin{verso}
By this process you Giant Rings,
Reveal to us the tiniest things.
\end{verso}

\hfill{29 September 2016}



\end{document}
